### 2024-01-15 inst/scripts/papertest.Rmd
fix sex assignment for auto pathways

pw=1
for(sb in c(.5,1)){
    print(pw)
    neutraltraitsParam$s[pw]=sb
    for(pre in c("v","h","o")){
        neutraltraitsParam$pre[pw:(pw+3),pre]=1
        pw=pw+1
        print(pw)
        neutraltraitsParam$s[pw]=sb
        for(post in c("h","o","i")){
            neutraltraitsParam$post[pw,post]=1
            print(pw)
            neutraltraitsParam$s[pw]=sb
            pw=pw+1
        }
    }
}

>>>>

pw=1
for(sb in c(.5,1)){
    print(pw)
    for(pre in c("v","h","o")){
        neutraltraitsParam$pre[pw:(pw+3),pre]=1
        neutraltraitsParam$s[pw:(pw+3)]=sb
        pw=pw+1
        print(pw)
        neutraltraitsParam$s[pw]=sb
        for(post in c("h","o","i")){
            neutraltraitsParam$post[pw,post]=1
            print(pw)
            neutraltraitsParam$s[pw]=sb
            pw=pw+1
        }
    }
}
